ESRC SDAI Application - Understanding domestic abuse using Big Data

### 2019-07-23 JeS_fields.tex
Pathways tinkering

Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, and health economics. \TM{Do we want to mention criminologists as well or are we trying to avoid having them as reviewers?}

Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation. Previous investigations focusing on domestic abuse in the context of the UK have either used police records \TM{Aren't we relying on police records? Can we make it clearer why we have a particular strength over those previous approaches?} or relied on a small-sample, qualitative approach.

@@

@@

As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers. The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.

>>>>

Owing to the variety of questions we aim to answer the diverse methodological approaches we will employ in addressing these questions, our research will deliver insights relevant to researchers across various social science disciplines, including psychology, behavioural scientists, criminology and health economics.

Psychologists working on understanding the risk factors of domestic abuse victimisation will benefit from the first quantitative, comprehensive, UK-based exploration of the risk factors of domestic abuse victimisation. Previous investigations focusing on domestic abuse in the context of the UK have either exclusively relied on police records or used a small-sample, qualitative approach. By drawing on multiple data sources, including police crime data and the CSEW, we can combine their strengths to validate previous findings and deliver new insights.

@@

Criminologists working on exploring the experiences of domestic abuse survivors in the Criminal Justice System will benefit from our research examining whether police mis-recording disproportionately affects certain victim groups.

@@

As Post-Doctoral researcher, Trendl will be responsible for performing the analyses upon the data, and leading the writing of the resulting papers. She will also be deeply involved with impact related activity. As an early career researcher, it is crucial that she be given the opportunity to expand her network, and attain these new skills. The demands of this project mean it is essential that this is a postdoctoral role, and that the individual has a strong track record in statistical analysis, with datasets such as the CSEW and WMP records.
